Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2018-12-21 SupportingInformation.Rmd
fixed minor error

<!--Display model selection results in a table-->
```{r tab_soilCNfit, echo=F, results="markup"}
#knitr::opts_knit$set(kable.force.latex = TRUE)
h<-BivMS_res_Loecke$InfCritRes[,c("copname","AICw","BICw","LT","UT")]
knitr::kable(h, #longtable = T, 
             format = "latex",
      caption.short = "Model fitting results for soil C and N dataset",
      caption = "Results of fitting our 16 copulas to the soil C and N dataset. Copula name abbreviations are given in the main text. AICw = AIC weight; BICw = BIC weight; LT = the lower-tail dependence statistic for the copula family with the fitted parameters; UT = the same for upper-tail dependence.\\label{tab_soilCNfit}",
      booktabs = TRUE)
```

>>>>

<!--Display model selection results in a table-->
```{r tab_soilCNfit, echo=F, results="markup"}
#knitr::opts_knit$set(kable.force.latex = TRUE)
h<-BivMS_res_Loecke$InfCritRes[,c("copname","AICw","BICw","LTdep","UTdep")]
colnames(h)<-c("copname","AICw","BICw","LT","UT")
knitr::kable(h, #longtable = T, 
             format = "latex",
      caption.short = "Model fitting results for soil C and N dataset",
      caption = "Results of fitting our 16 copulas to the soil C and N dataset. Copula name abbreviations are given in the main text. AICw = AIC weight; BICw = BIC weight; LT = the lower-tail dependence statistic for the copula family with the fitted parameters; UT = the same for upper-tail dependence.\\label{tab_soilCNfit}",
      booktabs = TRUE)
```
